Graphical Tests for Power Comparison of Competing Designs

### 2012-03-31 experiment.tex
tweaked results

Figure \ref{fig:conf} shows two barcharts of confidence levels by task, again coloring is used for correctness of answers. Euclidean displays lead to a very bimodal distribution of confidence: participants are either very sure or not sure at all of their answer. Confidence levels in polar charts are distributed much more uniformly.
\begin{figure}[hbtp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{conf-answer} 
   \caption{Barcharts of (subjective) confidence in answering correctly for each lineup. A strongly bimodal distribution is apparent, while confidence levels for polar charts are more uniform. There are only slight (and non significant) difference between confidence levels and correctness of results.}
   \label{fig:conf}
\end{figure}

@@

\begin{tabular}{cl}
\phantom{\includegraphics[width=0.03\linewidth]{Polar_Line.pdf}} & \vspace{-0.035in} \multirow{10}{*}{\hspace{-0.5in}\includegraphics[width=0.9\linewidth]{turk4-designs.pdf}} \\
\includegraphics[width=0.045\linewidth]{Polar_Line.pdf} \\
\includegraphics[width=0.045\linewidth]{Polar_NoLine.pdf} \\
\includegraphics[width=0.043\linewidth]{Euclidian_Line.pdf} \\
\includegraphics[width=0.043\linewidth]{Euclidian_NoLine.pdf}\\
\phantom{\includegraphics[width=0.13\linewidth]{Polar_Line.pdf}}\\
\includegraphics[width=0.045\linewidth]{Polar_Line.pdf} \\
\includegraphics[width=0.045\linewidth]{Polar_NoLine.pdf} \\
\includegraphics[width=0.043\linewidth]{Euclidian_Line.pdf} \\
\includegraphics[width=0.043\linewidth]{Euclidian_NoLine.pdf}\\
\phantom{\includegraphics[width=0.13\linewidth]{Polar_Line.pdf}}\\
  \end{tabular} 
  \vspace{0.1in}
   \caption{Power results for two competing designs: polar versus a Euclidean, with and without a reference line; facetting indicates sample size (as percentage of original data). Error bars indicate single Bonferroni adjusted 95\% confidence intervals. The two confidence intervals at the bottom of each panel shows a power comparison of Euclidean versus polar design according to eqn (\ref{eq:comp}). }
   \label{fig:treatment}
\end{figure}

>>>>

Figure \ref{fig:conf} shows two barcharts of confidence levels by task, again coloring is used for correctness of answers. Euclidean displays lead to a very bimodal distribution of confidence: participants are either very sure or not sure at all of their answer. Confidence levels in polar charts are distributed much more uniformly.
\begin{figure}[hbtp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{conf-answer} 
   \caption{Barcharts of self-reported confidence in answering correctly for each lineup. A strongly bimodal distribution is apparent, while confidence levels for polar charts are more uniform. There are only slight (and non significant) difference between confidence levels and correctness of results.}
   \label{fig:conf}
\end{figure}

@@

\begin{tabular}{cl}
\phantom{\includegraphics[width=0.03\linewidth]{Polar_Line.pdf}} & \vspace{-0.035in} \multirow{10}{*}{\hspace{-0.5in}\includegraphics[width=0.9\linewidth]{turk4-designs.pdf}} \\
\includegraphics[width=0.045\linewidth]{Polar_Line.pdf} \\
\includegraphics[width=0.045\linewidth]{Polar_NoLine.pdf} \\
\includegraphics[width=0.043\linewidth]{Euclidian_Line.pdf} \\
\includegraphics[width=0.043\linewidth]{Euclidian_NoLine.pdf}\\
\phantom{\includegraphics[width=0.13\linewidth]{Polar_Line.pdf}}\\
\includegraphics[width=0.045\linewidth]{Polar_Line.pdf} \\
\includegraphics[width=0.045\linewidth]{Polar_NoLine.pdf} \\
\includegraphics[width=0.043\linewidth]{Euclidian_Line.pdf} \\
\includegraphics[width=0.043\linewidth]{Euclidian_NoLine.pdf}\\
\phantom{\includegraphics[width=0.13\linewidth]{Polar_Line.pdf}}\\
  \end{tabular} 
  \vspace{0.1in}
   \caption{Power results for two competing designs: polar versus a Euclidean, with and without a reference line; facetting indicates sample size (as percentage of original data). Error bars indicate single Bonferroni adjusted 95\% confidence intervals. The two confidence intervals at the bottom of each panel shows a pairwise power comparison of Euclidean versus polar design according to eqn (\ref{eq:comp}). Differences from zero (vertical grey line) are of interest.}
   \label{fig:treatment}
\end{figure}
